\documentclass{article}

\begin{document}
    \begin{center}
        \textbf{Proposal for highschool tutoring}
    \end{center}

    \section*{Introduction}

    This proposal is to provide access to what I need to do and to have in the all-round type tutorial, including equipments and methodologies.

    \section*{General partition}

    Regarding to HKDSE syllabus, partitioning by half-year as follows:
    \begin{itemize}
        \item Number and algebra:\begin{enumerate}
            \item Algebraic notations handling and complex numbers;
            \item 解ving simple equations in one unknown;
            \item 解ving system of simple equations in two unknowns;
            \item 解ving quadratic equations in one unknown;
            \item Introducing functions and graphs;
            \item Exponentiation and logarithms;
            \item Handling polynomials;
            \item Variations;
            \item 解ving system of equations in advanced (More about equations);
            \item 解ving inequalities;
            \item Linear programming;
            \item Sequence and series.
        \end{enumerate}
        \item Locus:\begin{enumerate}
            \item Equation of straight lines;
            \item Distancing and variable location;
            \item Equation of circles;
            \item Equation of locus.
        \end{enumerate}
        \item Euclidean Geometry:\begin{enumerate}
            \item Trigonometry;
            \item Sine Law, Cosine Law and Heron's formula;
            \item Properties of circle;
            \item Area and Volume;
            \item 3-dimensional geometry.
        \end{enumerate}
        \item Data Handling:\begin{enumerate}
            \item Mean, mode, median, and standard deviation;
            \item Statistical charts reading;
            \item Counting;
            \item Probability;
            \item Statistical measure.
        \end{enumerate}
        \item Paper practising:\begin{enumerate}
            \item By-topic praticing;
            \item By-year praticing (CE);
            \item By-year praticing (HKDSE);
            \item Challenging practicing.
        \end{enumerate}
    \end{itemize}

    \subsubsection*{Cycle Routine}
    For each cycle, each students will have four lessons in total. The regular routine may follows
    \begin{itemize}
        \item One lesson as a thorough goal setting of the chapters and brief recalling of memories.
        \item two lessons on examples and practising with tutor guidance; and
        \item One lesson for test.
    \end{itemize}

    Each lesson consists of one hour and ten minutes. Details are included in later section.

    \subsubsection*{Equipment}
    \begin{itemize}
        \item Timetable
        \item Process checking (Score included)
        \item Teaching notes
        \item Test
        \item Comment sheet
    \end{itemize}
\end{document}