\documentclass{article}

\begin{document}
    \begin{center}
        Teaching plan
    \end{center}

    There are 14 cycles in one year, each cycle containing 4 lessons and should be taught and practice in depth.

    \noindent F.4:\begin{enumerate}
        \item Algebraic arithmetics, Surds and complex numbers.
        \item Rememberance of solving linear equations.
        \item Solving quadratic equations and understand relation between coefficients and roots.
        \item Learning functions and graphs of linear and quadratic equations.
        \item Polynomials.
        \item Variations.
        \item Equation of straight lines.
        \item Equation of circle.
        \item Locus
        \item Exponentiation and logarithms
        \item Graphs of Exponentiation and logarithms.
        \item Basic trigonometry in a circle.
        \item Solving equations in advanced.
    \end{enumerate}

    \noindent F.5:\begin{enumerate}
        \item inequalities.
        \item Linear programming.
        \item Sine Law, Cosine Law and Heron's formula.
        \item Properties of circle (Arc and angles)
        \item Properties of circle (Tangent lines)
        \item 3-dimensional geometry
        \item 3-dimensional geometry practice
        \item Mean, mode, median and standard deviation.
        \item Statistical chart reading.
        \item Counting.
        \item Probability.
        \item Probability.
        \item Statistical measure
    \end{enumerate}

    \noindent F.6:\begin{enumerate}
        \item AS and GS.
        \item Revisiting system of equations.
        \item Revisiting Geometry.
        \item Revisiting Data Handling.
        \item CE practice.
        \item CE practice.
        \item DSE practice.
        \item DSE practice.
    \end{enumerate}
\end{document}